\chapter{LITERATURE SURVEY}
\thispagestyle{empty}
\\
\hspace{.2cm}  IoT-based Smart Bin: In this paper IoT based smart bin has been developed
which can detect waste levels using ultrasonic sensors. Sends a warning message to the relevant authorities when the level exceeds the threshold value.
so that they can thoroughly clean the trash container. Not a chance of waste overflow and keeping the
environment clean and fresh. This paper can also monitor the smart bin using an
Android app [1]. Smart Bin for waste segregation and energy generation using the
Internet of Things: The IR sensor is employed in this study to estimate the level of waste deposition.Send a notification to the authority when waste accumulation reach a critical level. GPRS module is used to track the location of the bin that
needs to be replaced. GSM is used to send notifications. If the waste is no longer
extracted, the waste is sorted into biodegradable and non-biodegradable waste,
then the biodegradable waste is used to make fertilizer[2].\\ \\
\hspace{.2cm} IoT-Based Waste Management System for Smart City: State of every bin can
be monitored via WiFi. Rain sensors detect the presence of rainwater. Whenever
rainwater is detected, the lid of the bin will close automatically. When the trash can is full, it alerts the authorities.[3]. A cloud-based smart recycling
bin for waste Classification: Waste is classified using a Convolutional Neural Network (CNN) based on photos that have been taken. There are six categories of waste: cartons, glass, metal, paper, plastic, and trash. [4]. Using infrared sensors, an Internet of Things-based garbage collection system Garbage collection is carried out by creating real-time data on the level of completion of waste containers placed in various locations. [5]\\

Artificial Neural Network-based Intelligent Waste Segregator: An artificial
neural network is used to sort the waste into six classes using the captured image.
The classes are glass, metal, cardboard, paper, garbage and plastic. The creation of an automated waste sorting system is the aim of this paper. [6]. Waste is divided into three categories using an automatic waste separation and monitoring system.
Plastic, metal, and organic make up this trio. Detection of metal scrap is done using an Inductive Proximity Sensor. Sorting of wet and dry waste is carried out using a blower.
Plastic, paper etc. light waste can be sorted using this blower.[7].\\

\hspace{.2cm} Waste classification using random forests, Gaussian Na ̈ıve Bayes, support
vector Machine and Multilayer Perceptron: It's critical to recognise the waste types that can breakdown effectively. This article uses random forests, Gaussian Na ve Bayes, and SVM to classify a sizable dataset of biodegradable and non-biodegradable materials. The accuracy comparison of these models reveals that Random Forest has a high accuracy.[8].Intelligent waste management system
using deep learning with IoT: In this paper, the model has two significant parts.
The first part is an architectural model of waste classification and the second
part is the development of smart bins on IoT.Digestible waste and indigestible waste are the two main categories into which CNN typically separates garbage. Cardboard, glass, metal, paper, and other indigestible refuse are examples.[9]. Machine learning's use in waste management: Recognizing and classifying recyclable materials by utilising CNN, a neural network can categorise trash photos into plastic and non-plastic waste.[10].\\




\\\\


\begin{table}
    	\centering
    	\caption{Comparison between Related Works}
    	\label{table }
    	\begin{tabular}{|p{.7cm}|p{3.5cm}|p{2.5cm}|p{1cm}|p{5.7cm}|}
    		\hline
    		           Sl No  & Name of Paper &	Paper type & Year & Description \\
    		
    		\hline
    		1&
    	IOT Based Smart Bin & 
    		IRJET paper & 
    		2017 &
    Check the waste levels in the trash cans to see if they are full or not.
\\
    		\hline
    		2 &
    		Smart Bin for Waste Segregation and Energy
Generation using IoT
 &
    		IJERT paper &
    		2021&
    		The level of waste is determined using an IR sensor. Farmers will benefit since it can separate and digest the decomposable trash. \\
    		\hline
    		3&
    IOT Based Waste
Bin &
    		IRJET
 &
    		2020&Whether the trash can is full or not is determined using an ultrasonic sensor. The bin notifies the authority when it is full. A motor within the bin moves the door automatically.\\
    		\hline
    		4&
    	Smart Recycling
Bin for Waste
Classification&	
    		IEEE
&

    		2020&Based on the photographs that were taken, a convolution neural network was utilised to categorise garbage.\\
            \hline
            5&
           IoT based Waste
Collection System
using Infrared Sensors &
IEEE
&
            2016&
           Real-time information about the filling up of trash cans positioned at various far-off sites is generated during the waste collection procedure.  \\
            	\hline	
            6 &
           Artificial Neural Network-based IntelligentWaste Segregator &
            IJSER
 &
            2019 &
           Using photos, accurately identify and categorise a single waste material into six kinds.
\\
\hline
 


           
    		\end{tabular}
    \end{table}
    \newpage
    \begin{table}
    	\centering
    	\caption{Comparison between Related Works}
    	\label{table }
    	\begin{tabular}{|p{.7cm}|p{3.5cm}|p{2.5cm}|p{1cm}|p{5.7cm}|}
  	
            \hline
            7 & Automatic Waste
Segregator and
Monitoring System & STM
Journel & 2017 & Trash classification into three categories: metals, biological, and plastic.
An inductive proximity sensor is used to find the metallic waste. \\
\hline
8 & Classifying Wastes
Using Random
Forests, Gaussian
Na¨ıve Bayes and
Support Vector
Machine &IOP
Conference& 2020 & Images of rubbish can be divided into biodegradable and non-biodegradable categories using neural networks..\\
\hline
9 & Intelligent waste
management system
using deep
learning with IoT & Journal
of King
Saud
University & 2020 & Two key components: an IoT-based smart trash can for real-time garbage monitoring and an architectural model for waste classification.\\
\hline
10 & Application of
machine learning
to waste management& Research
Gate & 2017&CNN is used to classify waste photos into plastic and nonplastic categories using neural networks.\\
	\hline
    

   \end{tabular}
   \end{table}
   \\\\
   