




\begin{thebibliography}{99}

\bibitem{1}Fatma Taher et al.,"Lung Cancer Detection by Using Artificial Neural Network and Fuzzy Clustering Methods",
American Journal of Biomedical Engineering 2012, 2(3): 136-142
DOI: 10.5923/j.ajbe.20120203.08

\bibitem{2}Kiran S. Darne et al.," Use of Fuzzy C-Mean and Fuzzy Min-Max Neural Network in Lung Cancer Detection",
International Journal of Soft Computing and Engineering (IJSCE)
ISSN: 2231-2307, Volume-3, Issue-3, July 2013

\bibitem{3}Ada, Rajneet Kaur et al.i, "Early Detection and Prediction of Lung Cancer
Survival using Neural Network Classifier", International Journal of Application or Innovation in
 Engineering and Management(IJAIEM), vol. 2, issue. 6, June 2013

\bibitem{4}Gisele Helena Barboni Miranda et al., "Structural Analysis of Histological Images to Aid
Diagnosis of Cervical Cancer", 
International Journal of Computer Science, 
Engineering and Applications (IJCSEA) Vol.3, No.2, March 2012

\bibitem{5}M.E. Plissiti et al., "Automated segmentation of cell 
nuclei in PAP smear images",
American Medical Informatics Association
Annual Symposium, pp. 130-134, Nov. 2007.

\bibitem{6}Sajith Kecheril et al.,"Segmentation Of Lung 
Glandular Cells Using Multiple Color Spaces", International Journal of Computer Science, 
Engineering and Applications (IJCSEA) Vol.2, No.3, June 2012

\bibitem{7}Shekhar Singh et al.,"Breast Cancer detection and Classification using Neural Network",
(IJAEST)International Journal of Advanced Engineering Sciences and Technologies, Vol no. 6,Issue no. 1, 004-009,April 2012

\bibitem{8}Fatma Taher et al.,"Automatic Sputum Color Image Segmentation for Lung Cancer Diagnosis",
KSII Transactions on Iinternet and Information Systems Vol. 7, No. 1, Jan 2013

\bibitem{9}Fatma Taher et al., "A Thresholding Approach for Detection of Sputum Cell for
 Lung Cancer Early Diagnosis,”KSII Transactions on Iinternet and Information Systems Vol. 8, No. 2, Mar 2013

\bibitem{10}N.Werghi et al. ,"Segmentation of Sputum Cell Image for Early Lung Cance Detection", IEEE Signal Process. Lett., vol.
19, no. 4, pp. 199–202, Apr. 2012.

\bibitem{11}S. Issac Niwas et al.,"Complex wavelet as nucleus descriptors for Automated Cancer cytology
classifier system using ANN",American Journal of Biomedical Engineering 2010,
DOI: 10.5923/j.ajbe.20100203.08








\end{thebibliography}

























































 

